---
title: "Project 1"
output: html_document
---

This is the R markdown file for project 1.

Group members: Adam Humphrey, Travis Cox, Lola Shonaike

Here are the tables of customers, items, orders, and order details stored in data frames.

```{r}
source("../01 Data/Dataframe call.R", echo = TRUE)
```

Here are the plots for each table:

##Customers##
If you look to the left, their is Count Legend, with # of Customers from Califronia being 10.
```{r, echo=FALSE}
ggplot(customers, aes(x = CUSTOMER_STATE)) +
  geom_bar(width = 1, colour = "black") + coord_polar()
```

##Items##
This is a bar graph showing the how many albums a certain artist has for sale.
```{r, echo=FALSE}
ggplot(items, aes(x=ARTIST)) + geom_bar() + ylab("Number of Albums on sale") + xlab("Artist") + coord_flip()
```

##Orders##
This is a bar graph showing the number of orders placed by a customer with a certain customer id.
```{r, echo=FALSE}
ggplot(orders, aes(x=CUSTOMER_ID)) + geom_bar(fill="white",colour="darkgreen") + ylab("Number of Orders")+ scale_x_discrete("Customer ID")
                                                                                                                            
```

##Order details##
This graph shows the frequency of which each quantity of each item was sold.
EX: One copy of Umani in Concert was ordered 10 times, and two copies of Umani in Comcers were ordered once.
```{r, echo=FALSE}
source("../01 Data/Full data frame.R", echo = TRUE)
ggplot(order_details, aes(x = ITEM_ID, y = ORDER_QTY) ) + stat_sum(aes(group = 1, color = ITEM_ID))
```

##Reproducing given plots with accompanying R code##
Here are the plots with the R code used to recreat them.

Graph of order date by shipping date colored by unit price

###R code:###

ggplot(fulldf, aes(x = as.Date(ORDER_DATE, "%Y-%m-%d"), y = as.Date(SHIPPED_DATE, "%Y-%m-%d"), colour = as.factor(UNIT_PRICE))) + geom_point() + facet_wrap(~ CUSTOMER_STATE)

```{r, echo=FALSE}
ggplot(fulldf, aes(x = as.Date(ORDER_DATE, "%Y-%m-%d"), y = as.Date(SHIPPED_DATE, "%Y-%m-%d"), colour = as.factor(UNIT_PRICE))) + geom_point() + facet_wrap(~ CUSTOMER_STATE)
```

Graph of order date by shipping date colored by title of item

###R code:###

ggplot(fulldf, aes(x = as.Date(ORDER_DATE, "%Y-%m-%d"), y = as.Date(SHIPPED_DATE, "%Y-%m-%d"), colour = as.factor(TITLE))) + geom_point() + facet_wrap(~ CUSTOMER_STATE)

```{r, echo=FALSE}
ggplot(fulldf, aes(x = as.Date(ORDER_DATE, "%Y-%m-%d"), y = as.Date(SHIPPED_DATE, "%Y-%m-%d"), colour = as.factor(TITLE))) + geom_point() + facet_wrap(~ CUSTOMER_STATE)
```

Graph of order date by shipping date colored by artist

###R code:###

ggplot(fulldf, aes(x = as.Date(ORDER_DATE, "%Y-%m-%d"), y = as.Date(SHIPPED_DATE, "%Y-%m-%d"), colour = as.factor(ARTIST))) + geom_point() + facet_wrap(~ CUSTOMER_STATE)

```{r, echo=FALSE}
ggplot(fulldf, aes(x = as.Date(ORDER_DATE, "%Y-%m-%d"), y = as.Date(SHIPPED_DATE, "%Y-%m-%d"), colour = as.factor(ARTIST))) + geom_point() + facet_wrap(~ CUSTOMER_STATE)
```
